Trajectories

### 2021-09-15 Rmd/report.Rmd
Restore branch

# load packages
library(tidyverse)
library(gt)
library(lubridate)
library(wesanderson)
library(brms)
library(htmltools)
library(tidybayes)
library(scales)
library(patchwork)
library(janitor)
library(here)

# set params
theme_custom <- function(){
  theme_minimal() +
    theme(
      panel.grid = element_line(colour = "grey", linetype = "dotted"),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 12, colour = "black"),
      axis.text = element_text(colour = "black")
    )
}

theme_set(theme_custom())

# import data
items <- readRDS(here("Data", "items.rds"))
participants <- readRDS(here("Data", "participants.rds"))
responses <- readRDS(here("Data", "responses.rds"))

# import models
vocabulary <- readRDS(here("Data", "vocabulary.rds"))
vocabulary_long <- readRDS(here("Data", "vocabulary_long.rds"))
fit_prior <- readRDS(here("Results", "irt_2_prior.rds"))
fit <- readRDS(here("Results", "irt_2.rds"))

@@

  plot_layout(guides = "collect") &
  theme(
    legend.position = "top",
    legend.title = element_blank()
  ) &
  ggsave(here("Figures", "vocabulary_comprehension.png"))

@@

  plot_layout(guides = "collect") &
  theme(
    legend.position = "top",
    legend.title = element_blank()
  ) &
  ggsave(here("Figures", "vocabulary_production.png"))

@@

```{r vocabulary_long_comprehension, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary_long %>% 
  filter(type=="understands") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) +
  ggsave(here("Figures", "vocabulary_long_comprehension.png"))
```

@@

```{r vocabulary_long_production, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary_long %>% 
  filter(type=="produces") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) +
  ggsave(here("Figures", "vocabulary_long_production.png"))
```

@@

@@

m <- add_fitted_draws(nd, fit_prior, n = 20, re_formula = NA) %>% 
  mutate(frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")))

@@

ggplot(post, aes(.value)) +
  facet_wrap(~.variable, scales = "free_x") +
  geom_vline(xintercept = 0, size = 1, colour = "grey") +
  stat_histinterval(fill = "lightblue") +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_custom() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  ) +
  ggsave(here("Figures", "responses_fixed.png"))
```

>>>>

# load packages
library(targets)
library(tidyverse)
library(gt)
library(lubridate)
library(wesanderson)
library(brms)
library(htmltools)
library(tidybayes)
library(scales)
library(patchwork)
library(janitor)
library(here)

# set params
theme_set(theme_custom())

# import data
tar_load(items)
tar_load(participants)
tar_load(vocabulary)
tar_load(responses)
tar_load(fits)

@@

  plot_layout(guides = "collect") &
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

  plot_layout(guides = "collect") &
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

```{r vocabulary_long_comprehension, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary_long %>% 
  filter(type=="understands") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
```

@@

```{r vocabulary_long_production, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary_long %>% 
  filter(type=="produces") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
```

@@

## Raw data

```{r raw, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
responses %>%
  group_by(te, cognate) %>%
  summarise(
    understands = mean(understands, na.rm = TRUE),
    produces = mean(produces, na.rm = TRUE)
  ) %>%
  pivot_longer(
    c(understands, produces),
    names_to = "type",
    values_to = "prop"
  ) %>%
  mutate(type = str_to_sentence(type)) %>% 
  ggplot(aes(prop, reorder(te, -prop), colour = cognate)) +
  facet_wrap(vars(type)) +
  geom_vline(xintercept = 0.5, linetype = "dotted", size = 1) +
  geom_point(alpha = 0.5, size = 2) +
  labs(x = "Mean % of acquisition", y = "Translation equivalent ID", colour = "Type") +
  scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```

```{r raw_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
responses %>%
  mutate(age = as.factor(round(age))) %>% 
  group_by(te, age, cognate) %>%
  summarise(
    understands = mean(understands, na.rm = TRUE),
    produces = mean(produces, na.rm = TRUE)
  ) %>%
  pivot_longer(
    c(understands, produces),
    names_to = "type",
    values_to = "prop"
  ) %>%
  mutate(type = str_to_sentence(type)) %>% 
  ggplot(aes(age, prop, colour = cognate, fill = cognate, shape = cognate)) +
  facet_wrap(vars(type)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", size = 1) +
  geom_point(aes(group = interaction(age, cognate)), alpha = 0.5, size = 0.5) +
  stat_summary(fun.data = mean_se, geom = "pointrange") +
  labs(x = "Mean % of acquisition", y = "Translation equivalent ID",
       colour = "Cognate", shape = "Cognate", fill = "Cognate") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid = element_blank(),
    legend.title = element_blank()
  )
```

@@

m <- add_fitted_draws(nd, fits$fit_2, n = 20, re_formula = NA) %>% 
  mutate(frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")))

@@

ggplot(post, aes(.value)) +
  facet_wrap(~.variable, scales = "free_x") +
  geom_vline(xintercept = 0, size = 1, colour = "grey") +
  stat_histinterval(fill = "lightblue") +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_custom() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```
